---
title: "Can Exposure to Moral Foundations Affect Our Reactions to Policy Proposals?"
subtitle: "W241 Experiments and Causality (submitted December X, 2019)"
author: "Kevin Hartman, Hanna Rocks, Tim Spittle, and Jay Venkata"
date: "December 10, 2019"
tags: [T, B, D]
abstract: TBD
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown
  html_document:
    df_print: paged
    toc: yes
---

```{r setup, include = FALSE}
rm(list=ls())

packages = c('openxlsx'
             , 'tidyverse', 'data.table'
             , 'visNetwork'
             , 'lmtest', 'sandwich', 'car'
             , 'gridExtra', 'stargazer', 'cowplot', 'corrplot'
             , 'knitr')
lapply(packages, library, character.only = TRUE)

stargazer_type = "text" # change to latex when ready to knit
```

\pagebreak

# Background  
_[[TBD]]_  

# Data  
_[[TBD]]_  

```{r import}
# Pilot
# results_panel1_raw = read.xlsx("./data/pilot/survey_results_pilot_panel1.xlsx") %>% filter(StartDate != "Start Date")
# results_panel2_raw = read.xlsx("./data/pilot/survey_results_pilot_panel2.xlsx") %>% filter(StartDate != "Start Date")
# participant_detail_panel1 = read.csv("./data/pilot/participant_detail_pilot_panel1.csv", stringsAsFactors = FALSE)
# participant_detail_panel2 = read.csv("./data/pilot/participant_detail_pilot_panel2.csv", stringsAsFactors = FALSE)

# Study
results_panel1_raw = read.xlsx("./data/study/MF Framing Pilot - Full Recruitment - Panel 1_November 20, 2019_07.25.xlsx") %>% filter(!grepl("Start|Import", StartDate))
results_panel2_raw = read.xlsx("./data/study/MF Framing Pilot - Full Recruitment - Panel 2_November 20, 2019_07.26.xlsx") %>% filter(!grepl("Start|Import", StartDate))
participant_detail_panel1 = read.csv("./data/study/prolific_export_5dd4a350108b6748b25b5de1.csv", stringsAsFactors = FALSE)
participant_detail_panel2 = read.csv("./data/study/prolific_export_5dd4a34135582248315dfdca.csv", stringsAsFactors = FALSE)
```

### Data Cleaning  
_[[TBD]]_  [^1]  

[^1]: _[[Example footnote]]_  

```{r data_cleaning}
# Stack panel data
results_stacked = bind_rows(results_panel1_raw %>% mutate(panel = 1)
                            , results_panel2_raw %>% mutate(panel = 2)) %>%
  merge(bind_rows(participant_detail_panel1, participant_detail_panel2) %>% select(-session_id, -status, -age)
        , by.x = "PROLIFIC_PID"
        , by.y = "participant_id"
        , all.x = TRUE)

# Adjust all variable names to remove '-' and '.' + lowercase
names(results_stacked) = tolower(gsub(x = names(results_stacked), pattern = "\\-|\\.", replacement = "_"))

# Discrete variables as factors (manual ordering for plotting)
ideology_levels = c("Very Liberal", "Lean Liberal", "Liberal", "Moderate", "Conservative", "Lean Conservative", "Very Conservative")
ubi_group_levels = c("Promoter", "Passive", "Detractor")
ubi_familiarity_levels = c("Extremely familiar", "Very familiar", "Moderately familiar", "Slightly familiar", "Not familiar at all")

results_full = results_stacked  %>%
  # Define arms and nodes
  mutate(arm = case_when(grepl('a', fc_b_1, ignore.case = TRUE) ~ "purity_base"
                         , grepl('a', fc_c_1, ignore.case = TRUE) ~ "purity_extension"
                         , grepl('a', fc_d_1, ignore.case = TRUE) ~ "fairness_base"
                         , grepl('a', fc_e_1, ignore.case = TRUE) ~ "fairness_extension"
                         , TRUE ~ "control") %>% factor()
         , node = paste0(arm, "_panel_", panel)
         # Combine reaction vars from different arms
         , purity_self = case_when(grepl('a', fc_b_1, ignore.case = TRUE) ~ fc_b_1
                                 , TRUE ~ fc_c_1)
         , purity_repulsed = case_when(grepl('a', fc_b_2, ignore.case = TRUE) ~ fc_b_2
                                 , TRUE ~ fc_c_2)
         , purity_injustice = case_when(grepl('a', fc_b_3, ignore.case = TRUE) ~ fc_b_3
                                 , TRUE ~ fc_c_3)
         , purity_relieved = fc_c_4
         , fairness_self = case_when(grepl('a', fc_d_1, ignore.case = TRUE) ~ fc_d_1
                                 , TRUE ~ fc_e_1)
         , fairness_pain = case_when(grepl('a', fc_d_2, ignore.case = TRUE) ~ fc_d_2
                                     , TRUE ~ fc_e_2)
         , fairness_injustice = case_when(grepl('a', fc_d_3, ignore.case = TRUE) ~ fc_d_3
                                 , TRUE ~ fc_e_3)
         , fairness_relieved = fc_e_4
         , open_text_reaction = q3_fc2
         # Factor variables
         , ideology = factor(polispect, levels = ideology_levels)
         , ubi_group = factor(ubi_2_nps_group, levels = ubi_group_levels)
         , ubi_familiarity = factor(ubi_f, levels = ubi_familiarity_levels)
         # Numeric variables
         , ubi_number = as.numeric(ubi_2)) 

results_clean = results_full %>%
  select(prolific_pid, panel, arm, node
         , ideology, age, gender, urban, employment_status, student_status
         , purity_self, purity_repulsed, purity_injustice, purity_relieved
         , fairness_self, fairness_pain, fairness_injustice, fairness_relieved
         , open_text_reaction
         , ubi_number, ubi_group, ubi_familiarity)
```

## Exploratory Analysis  
_[[TBD]]_  

### Study Setup  

```{r exploratory, fig.height = 4, fig.width = 4, fig.align="center", fig.cap="Study Setup"}
arm_counts = results_clean %>%
  group_by(arm, panel, node) %>%
  summarise(count = n())

nodes = data.frame(
  id = 1:12
  , group = c("liberal", "conservative", arm_counts$arm)
  , label = c("liberal", "conservative", arm_counts$node)
  , value = c(sum(arm_counts$count[arm_counts$panel==1]), sum(arm_counts$count[arm_counts$panel==2]), arm_counts$count)
  # color, title, shape
  )

edges = data.frame(
  from = c(1, 2, 1, 2, 1, 2,  5, 6, 9,  10)
  , to = c(3, 4, 5, 6, 9, 10, 7, 8, 11, 12)
  )

visNetwork(nodes, edges) %>% 
  visHierarchicalLayout()
```

### Demographics  

```{r exploratory_demographics, fig.align="center", fig.cap="Demographics"}

grpstackbar_plot = ggplot() +
  facet_grid( ~ panel) +
  scale_fill_brewer(type = "div", palette = 5, direction = -1, aesthetics = "fill") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Ideology
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(ideology, panel) %>% summarise(count = n())
           , aes(x = ideology, y = count, fill = ideology)
           , stat = "identity") 
# Age
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(age, ideology, panel) %>% summarise(count = n())
           , aes(x = age, y = count, fill = ideology)
           , stat = "identity") 

# Gender
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(gender, ideology, panel) %>% summarise(count = n())
           , aes(x = gender, y = count, fill = ideology)
           , stat = "identity") 

# Urban
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(urban, ideology, panel) %>% summarise(count = n())
           , aes(x = urban, y = count, fill = ideology)
           , stat = "identity") 
```

Example reference to r cell _\autoref{fig:exploratory_demographics}_ shows _[[TBD]]_   

### Reactions  

```{r exploratory_reactions, fig.align="center", fig.cap="Reactions"}

# results_clean %>% filter(arm == "purity_base") %>% group_by(ideology, panel, purity_self) %>% summarise(count = n())
# grpstackbar_plot +
#   geom_bar(data = results_clean %>% filter(arm == "purity_base") %>% group_by(ideology, panel, purity_self) %>% summarise(count = n())
#            , aes(x = purity_self, y = count, fill = ideology)
#            , stat = "identity") 

results_response_melt = results_clean %>% select(panel, arm, purity_self, purity_repulsed, purity_injustice, purity_relieved) %>%
  melt(id.vars = c("panel", "arm")
       , measure.vars = c("purity_self", "purity_repulsed", "purity_injustice", "purity_relieved")
       , variable.name = "prompt"
  ) %>%
  filter(!is.na(value)) %>%
  group_by(panel, arm, prompt, value) %>% summarise(count = n()) 

#### TO DO - spread to wide ####
  # spread(key = c("panel", "arm", "prompt")
  #        , value = count)
```

### Outcome  

```{r exploratory_outcome, fig.align="center", fig.cap="Outcomes"}
# Histogram of familiarity
ggplot(data = results_clean %>% group_by(ubi_familiarity, ideology, panel) %>% summarise(count = n())
       , aes(x = ubi_familiarity, y = count, fill = ideology)) +
  geom_bar(stat="identity") + 
  facet_grid( ~ panel) +
  scale_fill_brewer(type = "div", palette = 5, direction = -1, aesthetics = "fill") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# Heat map of number UBI like
ggplot(data = results_clean %>% group_by(ubi_familiarity, ideology) %>% summarise(ubi_number_avg = mean(ubi_number))
       , aes(x = ubi_familiarity, y = ideology, fill = ubi_number_avg)) +
  geom_tile() +
  scale_fill_distiller(direction = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

\pagebreak

# Methodology  

## Model 1  

**Independent variable**  

**Dependent variable**  

**Model specification**  

_[[TBD]]_. (see _\autoref{fig:model_1_explore}_)

```{r methodology_model_1_explore, fig.height = 3, fig.width = 4, fig.align="center", fig.cap="\\label{fig:model_1_explore}Model 1 - Exploratory Plot"}
# Exploratory
model_1_purity_base = lm(ubi_number ~ arm, data = results_full %>% filter(arm %in% c("control", "purity_base") & panel == 1))
model_1_purity_ext = lm(ubi_number ~ arm, data = results_full %>% filter(arm %in% c("control", "purity_extension") & panel == 1))
model_2_purity_base = lm(ubi_number ~ arm, data = results_full %>% filter(arm %in% c("control", "purity_base") & panel == 2))
model_2_purity_ext = lm(ubi_number ~ arm, data = results_full %>% filter(arm %in% c("control", "purity_extension") & panel == 2))

stargazer(model_1_purity_base, model_1_purity_ext, model_2_purity_base, model_2_purity_ext
          , column.labels = c("P1, Purity Base", "P1, Purity Ext", "P2, Purity Base", "P2, Purity Ext")
          , type = stargazer_type) 

```

```{r methodology_model_1}
model_1 = lm(ubi_number ~ arm+panel, data = results_full)

stargazer(model_1, type = stargazer_type) 
```

_[[Example Table]]_  

| Model | Specification | Interpretation | Figure |
| :--- | :------ | :-------- | :--- |
| Model 1 | _crmrte~prbarr_ | $\Delta crmrte = \beta_1 \Delta prbarr$ | _\autoref{fig:model_1_fitplots}_ |

```{r methodology_model_1_final, results='asis', fig.cap="\\label{fig:model_1_final}"}
# Stargazer
```

\pagebreak

# Results  

_[[TBD]]_  

\pagebreak

# Conclusion  

_[[TBD]]_  

\pagebreak

# Discussion

_[[TBD]]_  

## Limitations

_[[TBD]]_   

\pagebreak

# Technical Appendix

## Data Dictionary

| Variable Name | Variable | Values | Source | Notes |
| :---- | :-------- | :-------- | :---------- | :----- |
| county | County ID | Odd Integers || Few missing |

\pagebreak

## Exploratory Data Analysis

**Additional steps taken not included in the body of the report**  

_[[TBD]]_  
