---
title: "Can Exposure to Moral Foundations Affect Our Reactions to Policy Proposals?"
subtitle: "W241 Experiments and Causality (submitted December X, 2019)"
author: "Kevin Hartman, Hanna Rocks, Tim Spittle, and Jay Venkata"
date: "December 10, 2019"
tags: [T, B, D]
abstract: TBD
output:
  html_document:
    df_print: paged
    toc: yes
  md_document:
    variant: markdown
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
---

```{r setup, include = FALSE}
rm(list=ls())

packages = c('openxlsx'
             , 'tidyverse', 'data.table'
             , 'visNetwork'
             , 'lmtest', 'sandwich', 'car'
             , 'gridExtra', 'stargazer', 'cowplot', 'corrplot'
             , 'knitr')
lapply(packages, library, character.only = TRUE)

stargazer_type = "text" # change to latex when ready to knit
```

\pagebreak

# Background  
_[[TBD]]_  

# Data  
_[[TBD]]_  

```{r import}
# Pilot
# results_panel1_raw = read.xlsx("./data/pilot/survey_results_pilot_panel1.xlsx") %>% filter(StartDate != "Start Date")
# results_panel2_raw = read.xlsx("./data/pilot/survey_results_pilot_panel2.xlsx") %>% filter(StartDate != "Start Date")
# participant_detail_panel1 = read.csv("./data/pilot/participant_detail_pilot_panel1.csv", stringsAsFactors = FALSE)
# participant_detail_panel2 = read.csv("./data/pilot/participant_detail_pilot_panel2.csv", stringsAsFactors = FALSE)

# Study
results_panel1_raw = read.xlsx("./data/study/MF Framing Pilot - Full Recruitment - Panel 1_November 20, 2019_07.25.xlsx") %>% filter(!grepl("Start|Import", StartDate))
results_panel2_raw = read.xlsx("./data/study/MF Framing Pilot - Full Recruitment - Panel 2_November 20, 2019_07.26.xlsx") %>% filter(!grepl("Start|Import", StartDate))
participant_detail_panel1 = read.csv("./data/study/prolific_export_5dd4a350108b6748b25b5de1.csv", stringsAsFactors = FALSE)
participant_detail_panel2 = read.csv("./data/study/prolific_export_5dd4a34135582248315dfdca.csv", stringsAsFactors = FALSE)
```

### Data Cleaning  
_[[TBD]]_  [^1]  

[^1]: _[[Example footnote]]_  

```{r data_cleaning}
# Stack panel data
results_stacked = bind_rows(results_panel1_raw %>% mutate(panel = 1)
                            , results_panel2_raw %>% mutate(panel = 2)) %>%
  merge(bind_rows(participant_detail_panel1, participant_detail_panel2) %>% select(-session_id, -status, -age)
        , by.x = "PROLIFIC_PID"
        , by.y = "participant_id"
        , all.x = TRUE)

# Adjust all variable names to remove '-' and '.' + lowercase
names(results_stacked) = tolower(gsub(x = names(results_stacked), pattern = "\\-|\\.", replacement = "_"))

# Discrete variables as factors (manual ordering for plotting)
ideology_levels = c("Very Liberal", "Lean Liberal", "Liberal", "Moderate", "Conservative", "Lean Conservative", "Very Conservative")
ubi_group_levels = c("Promoter", "Passive", "Detractor")
ubi_familiarity_levels = c("Extremely familiar", "Very familiar", "Moderately familiar", "Slightly familiar", "Not familiar at all")

results_full = results_stacked  %>%
  # Define arms and nodes
  mutate(arm = case_when(grepl('a', fc_b_1, ignore.case = TRUE) ~ "purity_base"
                         , grepl('a', fc_c_1, ignore.case = TRUE) ~ "purity_extension"
                         , grepl('a', fc_d_1, ignore.case = TRUE) ~ "fairness_base"
                         , grepl('a', fc_e_1, ignore.case = TRUE) ~ "fairness_extension"
                         , TRUE ~ "control") %>% factor()
         , node = paste0(arm, "_panel_", panel)
         # Combine reaction vars from different arms
         , purity_q1_self = case_when(grepl('a', fc_b_1, ignore.case = TRUE) ~ fc_b_1
                                 , TRUE ~ fc_c_1)
         , purity_q2_repulsed = case_when(grepl('a', fc_b_2, ignore.case = TRUE) ~ fc_b_2
                                 , TRUE ~ fc_c_2)
         , purity_q3_injustice = case_when(grepl('a', fc_b_3, ignore.case = TRUE) ~ fc_b_3
                                 , TRUE ~ fc_c_3)
         , purity_q4_relieved = fc_c_4
         , fairness_q1_self = case_when(grepl('a', fc_d_1, ignore.case = TRUE) ~ fc_d_1
                                 , TRUE ~ fc_e_1)
         , fairness_q2_pain = case_when(grepl('a', fc_d_2, ignore.case = TRUE) ~ fc_d_2
                                     , TRUE ~ fc_e_2)
         , fairness_q3_injustice = case_when(grepl('a', fc_d_3, ignore.case = TRUE) ~ fc_d_3
                                 , TRUE ~ fc_e_3)
         , fairness_q4_relieved = fc_e_4
         , open_text_reaction = q3_fc2
         # Factor variables
         , ideology = factor(polispect, levels = ideology_levels)
         , ideology_bin = case_when(is.na(ideology) ~ "missing"
                                    , ideology == "Very Liberal" ~ "liberal"
                                    , ideology == "Lean Liberal" ~ "liberal"
                                    , ideology == "Liberal" ~ "liberal"
                                    , ideology == "Very Conservative" ~ "conservative"
                                    , ideology == "Lean Conservative" ~ "conservative"
                                    , ideology == "Conservative" ~ "conservative"
                                    , TRUE ~ "moderate")
         , ubi_group = factor(ubi_2_nps_group, levels = ubi_group_levels)
         , ubi_familiarity = factor(ubi_f, levels = ubi_familiarity_levels)
         # Numeric variables
         , ubi_number = as.numeric(ubi_2))

results_clean = results_full %>%
  select(prolific_pid, panel, arm, node
         , ideology, ideology_bin, age, gender, urban, employment_status, student_status
         , purity_q1_self, purity_q2_repulsed, purity_q3_injustice, purity_q4_relieved
         , fairness_q1_self, fairness_q2_pain, fairness_q3_injustice, fairness_q4_relieved
         , open_text_reaction
         , ubi_number, ubi_group, ubi_familiarity)
```

## Exploratory Analysis  
_[[TBD]]_  

### Study Setup  

```{r exploratory, fig.height = 4, fig.width = 4, fig.align="center", fig.cap="Study Setup"}
arm_counts = results_clean %>%
  group_by(arm, panel, node) %>%
  summarise(count = n())

nodes = data.frame(
  id = 1:12
  , group = c("liberal", "conservative", arm_counts$arm)
  , label = c("liberal", "conservative", arm_counts$node)
  , value = c(sum(arm_counts$count[arm_counts$panel==1]), sum(arm_counts$count[arm_counts$panel==2]), arm_counts$count)
  # color, title, shape
  )

edges = data.frame(
  from = c(1, 2, 1, 2, 1, 2,  5, 6, 9,  10)
  , to = c(3, 4, 5, 6, 9, 10, 7, 8, 11, 12)
  )

visNetwork(nodes, edges) %>%
  visHierarchicalLayout()
```

### Demographics  

```{r exploratory_demographics, fig.align="center", fig.cap="Demographics"}

grpstackbar_plot = ggplot() +
  facet_grid( ~ panel) +
  scale_fill_brewer(type = "div", palette = 5, direction = -1, aesthetics = "fill") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Ideology
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(ideology, panel) %>% summarise(count = n())
           , aes(x = ideology, y = count, fill = ideology)
           , stat = "identity")
# Age
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(age, ideology, panel) %>% summarise(count = n())
           , aes(x = age, y = count, fill = ideology)
           , stat = "identity")

# Gender
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(gender, ideology, panel) %>% summarise(count = n())
           , aes(x = gender, y = count, fill = ideology)
           , stat = "identity")

# Urban
grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(urban, ideology, panel) %>% summarise(count = n())
           , aes(x = urban, y = count, fill = ideology)
           , stat = "identity")
```

Example reference to r cell _\autoref{fig:exploratory_demographics}_ shows _[[TBD]]_   

### Reactions  

```{r exploratory_reactions, fig.align="center", fig.cap="Reactions"}
results_response = results_clean %>%
  select(panel, arm
         , purity_q1_self, purity_q2_repulsed, purity_q3_injustice, purity_q4_relieved
         , fairness_q1_self, fairness_q2_pain, fairness_q3_injustice, fairness_q4_relieved) %>%
  gather(prompt, value, -panel, -arm) %>%
  filter(!is.na(value)) %>%
  group_by(panel, arm, prompt, value) %>% summarise(count = n()) #%>%
  # spread(value, count) %>%
  # arrange(panel, arm, prompt) %>%
  # select("panel", "arm", "prompt", "A great deal", "A lot", "A moderate amount", "A little", "None at all")

ggplot(data = results_response
       , aes(x = prompt, y = value, fill = count)) +
  geom_tile() +
  facet_grid(rows = vars(arm), cols = vars(panel)) +
  scale_fill_distiller(direction = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Outcome  

```{r exploratory_outcome, fig.align="center", fig.cap="Outcomes"}
# Histogram of familiarity
ggplot(data = results_clean %>% group_by(ubi_familiarity, ideology, panel) %>% summarise(count = n())
       , aes(x = ubi_familiarity, y = count, fill = ideology)) +
  geom_bar(stat="identity") +
  facet_grid( ~ panel) +
  scale_fill_brewer(type = "div", palette = 5, direction = -1, aesthetics = "fill") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Heat map of number UBI like
ggplot(data = results_clean %>% group_by(ubi_familiarity, ideology) %>% summarise(ubi_number_avg = mean(ubi_number))
       , aes(x = ubi_familiarity, y = ideology, fill = ubi_number_avg)) +
  geom_tile() +
  scale_fill_distiller(direction = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

\pagebreak

# Methodology  

## Model 1  

**Independent variable**  

**Dependent variable**  

**Model specification**  

_[[TBD]]_. (see _\autoref{fig:model_1_explore}_)

```{r lm_function}
my_lm_calcs = function(lm_in, clusters_in){
  # Robust
  vcov_robust = vcovHC(lm_in)
  se_robust = sqrt(diag(vcov_robust))
  # Cluster
  if(length(clusters_in) > 1){
    vcov_cluster = cluster.vcov(lm_in, clusters_in)
    se_cluster = sqrt(diag(vcov_cluster))
  } else {
    vcov_cluster = NA
    se_cluster = NA
  }
  # Output
  lm_out = list(lm = lm_in
                , vcov_robust = vcov_robust
                , se_robust = se_robust
                , vcov_cluster = vcov_cluster
                , se_cluster = se_cluster
  )
  return(lm_out)
}
```

```{r}
# Summaries
all_data = data.table(results_full)
all_data[ , .(ubi=mean(as.numeric(ubi_2))), by=list(panel, arm) ]
all_data[, ideology_bin := case_when(is.na(ideology) ~ "missing",
                                           ideology=="Very Liberal" ~ "liberal",
                                           ideology=="Lean Liberal" ~ "liberal",
                                           ideology=="Liberal" ~ "liberal",
                                           ideology=="Very Conservative" ~ "conservative",
                                           ideology=="Lean Conservative" ~ "conservative",
                                           ideology=="Conservative" ~ "conservative",
                                           TRUE ~ "moderate"), ]
all_data[, story := case_when(is.na(arm) ~ "missing",
                                           arm=="control" ~ "",
                                           arm=="purity_base" ~ "homeless",
                                           arm=="purity_extension" ~ "homeless-cleaned",
                                           arm=="care_base" ~ "bullying",
                                           arm=="care_extension" ~ "bullying-addressed",
                                           TRUE ~ "others"), ]
all_data[, FemaleReader := ifelse(gender!='Male', 1, 0), ]
all_data[, ubi := as.numeric(ubi_2), ]
```

```{r}
# augment model with results from coefteest and coefci using 
# the supplied variance/covariance matrix
apply_robust_estimates = function(model, vcovmatrix) {
  model$robust.coeftest = coeftest(model, vcov. = vcovmatrix)
  model$robust.estimate = model$robust.coeftest[, 'Estimate']
  model$robust.std.error = model$robust.coeftest[, 'Std. Error']
  model$robust.statistic = model$robust.coeftest[, 't value']
  model$robust.p.value = model$robust.coeftest[, 'Pr(>|t|)']
  model$robust.coefci = coefci(model, vcov. = vcovmatrix)
  model$robust.ci.low = model$robust.coefci[, "2.5 %"]
  model$robust.ci.high = model$robust.coefci[, "97.5 %"]
  model
}
# liberals - homeless story
hom_lib_mod<-all_data[ ideology_bin=='liberal' & story != 'bullying' & story != 'bullying-addressed',  lm(ubi~story*FemaleReader)]
hom_lib_mod<-apply_robust_estimates(hom_lib_mod, vcovHC(hom_lib_mod))
# conservatives - homeless story
hom_con_mod<-all_data[ ideology_bin=='conservative' & story != 'bullying' & story != 'bullying-addressed',  lm(ubi~story*FemaleReader)]
hom_con_mod<-apply_robust_estimates(hom_con_mod, vcovHC(hom_con_mod))
# liberals - jacket story
jac_lib_mod<-all_data[ ideology_bin=='liberal' & story != 'homeless' & story != 'homeless-cleaned',  lm(ubi~story*FemaleReader)]
jac_lib_mod<-apply_robust_estimates(jac_lib_mod, vcovHC(jac_lib_mod))
# conservatives - jacket story
jac_con_mod<-all_data[ ideology_bin=='conservative' & story != 'homeless' & story != 'homeless-cleaned',  lm(ubi~story*FemaleReader)]
jac_con_mod<-apply_robust_estimates(jac_con_mod, vcovHC(jac_con_mod))
stargazer(hom_lib_mod, hom_con_mod,
          type = 'text', 
          se = list(sqrt(diag(vcovHC(hom_lib_mod))),
                    sqrt(diag(vcovHC(hom_con_mod)))), 
          header=F,
          report=('v*c*sp'), 
          add.lines=list(c("Ideology", "Liberal", "Conservative")))
stargazer(jac_lib_mod, jac_con_mod,
          type = 'text', 
          se = list(sqrt(diag(vcovHC(jac_lib_mod))),
                    sqrt(diag(vcovHC(jac_con_mod)))), 
          header=F,
          report=('v*c*sp'), 
          add.lines=list(c("Ideology", "Liberal", "Conservative")))
```

```{r methodology_model_1_explore, fig.height = 3, fig.width = 4, fig.align="center", fig.cap="\\label{fig:model_1_explore}Model 1 - Exploratory Plot"}
# Exploratory
model1_liberal = my_lm_calcs(lm_in = lm(ubi_number ~ arm, data = results_clean %>% filter(ideology_bin == 'liberal')), clusters_in = NA)
model1_conservative = my_lm_calcs(lm_in = lm(ubi_number ~ arm, data = results_clean %>% filter(ideology_bin == 'conservative')), clusters_in = NA)

stargazer(model1_liberal$lm, model1_conservative$lm
          , type = stargazer_type, header = F
          , se = list(model1_liberal$se_robust, model1_conservative$se_robust)
          , title = "Moral Foundations Prelim Regression Specifications"
          , column.labels = c("Liberals", "Conservative")
          , notes = "HC Robust Standard Errors"
          , report = ('v*c*sp')
)
```

```{r methodology_model_1}
model_1 = lm(ubi_number ~ arm+ideology_bin, data = results_full)

stargazer(model_1, type = stargazer_type)
```

```{r random_specs}

model1_liberal_gender = my_lm_calcs(lm_in = lm(ubi_number ~ arm*gender, data = results_clean %>% filter(ideology_bin == 'liberal')), clusters_in = NA)
model1_conservative_gender = my_lm_calcs(lm_in = lm(ubi_number ~ arm*gender, data = results_clean %>% filter(ideology_bin == 'conservative')), clusters_in = NA)

stargazer(model1_liberal_gender$lm, model1_conservative_gender$lm
          , type = stargazer_type, header = F
          , se = list(model1_liberal_gender$se_robust, model1_conservative_gender$se_robust)
          , title = "Moral Foundations Prelim Regression Specifications"
          , column.labels = c("Liberals", "Conservative")
          , notes = "HC Robust Standard Errors"
          , report = ('v*c*sp')
)
```

_[[Example Table]]_  

| Model | Specification | Interpretation | Figure |
| :--- | :------ | :-------- | :--- |
| Model 1 | _crmrte~prbarr_ | $\Delta crmrte = \beta_1 \Delta prbarr$ | _\autoref{fig:model_1_fitplots}_ |

```{r methodology_model_1_final, results='asis', fig.cap="\\label{fig:model_1_final}"}
# Stargazer
```

\pagebreak

# Results  

_[[TBD]]_  

\pagebreak

# Conclusion  

_[[TBD]]_  

\pagebreak

# Discussion

_[[TBD]]_  

## Limitations

_[[TBD]]_   

\pagebreak

# Technical Appendix

## Data Dictionary

| Variable Name | Variable | Values | Source | Notes |
| :---- | :-------- | :-------- | :---------- | :----- |
| county | County ID | Odd Integers || Few missing |

\pagebreak

## Exploratory Data Analysis

**Additional steps taken not included in the body of the report**  

_[[TBD]]_  
