---
title: "Can Exposure to Moral Foundations Affect Our Reactions to Policy Proposals?"
subtitle: "W241 Experiments and Causality (submitted December X, 2019)"
author: "Kevin Hartman, Hanna Rocks, Tim Spittle, and Jay Venkata"
date: "December 10, 2019"
tags: [T, B, D]
abstract: TBD
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown
  html_document:
    df_print: paged
    toc: yes
---

```{r setup, include = FALSE}
rm(list=ls())

packages = c('openxlsx'
             , 'tidyverse', 'data.table'
             , 'visNetwork'
             , 'lmtest', 'sandwich', 'car'
             , 'gridExtra', 'stargazer', 'cowplot', 'corrplot'
             , 'knitr')
lapply(packages, library, character.only = TRUE)

# install.packages("webshot")
# webshot::install_phantomjs()

stargazer_type = "text" # change to latex when ready to knit
```

\pagebreak

# Background  
_[[TBD]]_  

# Data  
_[[TBD]]_  

```{r import, include = FALSE}
# Survey Results
# Panel 1
results_raw_panel1 = read.csv("./data/study/MF Framing Pilot - Full Recruitment - Panel 1.csv", stringsAsFactors = FALSE) %>%   filter(!grepl("Start|Import", StartDate)) %>% 
  mutate(panel = 1)
# Panel 2 
results_raw_panel2 = read.csv("./data/study/MF Framing Pilot - Full Recruitment - Panel 2.csv", stringsAsFactors = FALSE) %>%
  filter(!grepl("Start|Import", StartDate)) %>% 
  mutate(panel = 2)
# Panel 2 - 10 Control Females
results_raw_panel2_10fem = read.csv("./data/study/MF Framing Pilot - Full Recruitment - Panel 2 - 10 Female Control.csv", stringsAsFactors = FALSE) %>% 
  filter(!grepl("Start|Import", StartDate)) %>% 
  mutate(panel = 2)

# Participant Details
# Panel 1
participant_detail_panel1 = read.csv("./data/study/Prolific Participants - Panel 1.csv", stringsAsFactors = FALSE)
participant_detail_panel2 = read.csv("./data/study/Prolific Participants - Panel 2.csv", stringsAsFactors = FALSE)
participant_detail_panel2_10fem = read.csv("./data/study/Prolific Participants - Panel 2 - 10 Female Control.csv", stringsAsFactors = FALSE)
```

```{r deduplicate, include = FALSE}
# Stack panel data (510 obs x 63 vars)
results_stacked = bind_rows(results_raw_panel1
                            , results_raw_panel2
                            , results_raw_panel2_10fem
                            ) %>%
  # Duplicate responses are a product of our multiple data extracts, remove as-is 510 obs x 63 vars)
  distinct(ResponseId, .keep_all= TRUE)
# Identify if the same person filled out the survey >1x
results_ids_dedup = results_stacked %>%
  select(PROLIFIC_PID, ResponseId, StartDate) %>%
  group_by(PROLIFIC_PID) %>%
  summarize(count = n()
            , min_date = min(StartDate))
# Keep only their first submission (505 obs x 64 vars [count will tell us who filled out 2x])
results_dedup = results_stacked %>%
  merge(results_ids_dedup
        , by.x = c("PROLIFIC_PID", "StartDate")
        , by.y = c("PROLIFIC_PID", "min_date")
        , all.x = TRUE) %>%
  filter(!is.na(count))

# Stack participant details (518 obs x 21 vars)
participaipant_detail_stacked =  bind_rows(participant_detail_panel1
                  , participant_detail_panel2
                  , participant_detail_panel2_10fem)  %>%
  # Duplicate responses are a product of our multiple data extracts, remove as-is (518 obs x 21 vars)
  distinct(session_id, .keep_all= TRUE) %>%
  # Remove vars that will be in results as well (518 obs x 19 vars)
  select(-status, -age)
# Identify if the same person filled out the survey >1x
participaipant_ids_dedup = participaipant_detail_stacked %>%
  select(participant_id, session_id, started_datetime) %>%
  group_by(participant_id) %>%
  summarize(count = n()
            , min_date = min(started_datetime))
# Keep only their first submission (513 obs x 18 vars [count will tell us who filled out 2x])
participaipant_detail_dedup = participaipant_detail_stacked %>%
  merge(participaipant_ids_dedup
        , by.x = c("participant_id", "started_datetime")
        , by.y = c("participant_id", "min_date")
        , all.x = TRUE) %>%
  filter(!is.na(count)) %>% select(-count, -session_id)

# Merge for final dataset (505 obs x 81 vars)
results_full_dedup = merge(results_dedup
                           , participaipant_detail_dedup
                           , by.x = "PROLIFIC_PID"
                           , by.y = "participant_id"
                           , all.x = TRUE)
```

### Data Cleaning  
_[[TBD]]_  [^1]  

[^1]: _[[Example footnote]]_  

```{r data_cleaning, include = FALSE}
# Adjust all variable names to remove '-' and '.' + lowercase
names(results_full_dedup) = tolower(gsub(x = names(results_full_dedup), pattern = "\\-|\\.", replacement = "_"))

# Discrete variables as factors (manual ordering for plotting)
ideology_levels = c("Very Liberal", "Lean Liberal", "Liberal", "Moderate", "Conservative", "Lean Conservative", "Very Conservative")
response_levels = c("A great deal", "A lot", "A moderate amount", "A little", "None at all")
ubi_group_levels = c("Promoter", "Passive", "Detractor")
ubi_familiarity_levels = c("Extremely familiar", "Very familiar", "Moderately familiar", "Slightly familiar", "Not familiar at all")

results_full = results_full_dedup  %>%
  # Define arms and nodes
  mutate(arm = case_when(grepl('a', fc_b_1, ignore.case = TRUE) ~ "purity_base"
                         , grepl('a', fc_c_1, ignore.case = TRUE) ~ "purity_extension"
                         , grepl('a', fc_d_1, ignore.case = TRUE) ~ "fairness_base"
                         , grepl('a', fc_e_1, ignore.case = TRUE) ~ "fairness_extension"
                         , TRUE ~ "control") %>% factor(levels = c("control", "purity_base", "purity_extension", "fairness_base", "fairness_extension"))
         , node = paste0(arm, "_panel_", panel)
         , arm_level = case_when(grepl('base', arm) ~ 'base'
                                 , grepl('extension', arm) ~ 'extension'
                                 , TRUE ~ 'control') %>% factor(levels = c("control", "base", "extension"))
         # Combine reaction vars from different arms
         , purity_q1_self = case_when(grepl('a', fc_b_1, ignore.case = TRUE) ~ fc_b_1
                                      , grepl('a', fc_c_1, ignore.case = TRUE) ~ fc_c_1
                                      , TRUE ~ NA_character_)
         , purity_q2_repulsed = case_when(grepl('a', fc_b_2, ignore.case = TRUE) ~ fc_b_2
                                          , grepl('a', fc_c_2, ignore.case = TRUE) ~ fc_c_2
                                          , TRUE ~ NA_character_)
         , purity_q3_injustice = case_when(grepl('a', fc_b_3, ignore.case = TRUE) ~ fc_b_3
                                           , grepl('a', fc_c_3, ignore.case = TRUE) ~ fc_c_3
                                           , TRUE ~ NA_character_)
         , purity_q4_relieved = case_when(grepl('a', fc_c_4, ignore.case = TRUE) ~ fc_c_4
                                          , TRUE ~ NA_character_)
         , fairness_q1_self = case_when(grepl('a', fc_d_1, ignore.case = TRUE) ~ fc_d_1
                                        , grepl('a', fc_e_1, ignore.case = TRUE) ~ fc_e_1
                                        , TRUE ~ NA_character_)
         , fairness_q2_pain = case_when(grepl('a', fc_d_2, ignore.case = TRUE) ~ fc_d_2
                                        , grepl('a', fc_e_2, ignore.case = TRUE) ~ fc_e_2
                                        , TRUE ~ NA_character_)
         , fairness_q3_injustice = case_when(grepl('a', fc_d_3, ignore.case = TRUE) ~ fc_d_3
                                             , grepl('a', fc_e_3, ignore.case = TRUE) ~ fc_e_3
                                             , TRUE ~ NA_character_)
         , fairness_q4_relieved = case_when(grepl('a', fc_e_4, ignore.case = TRUE) ~ fc_e_4
                                          , TRUE ~ NA_character_)
         # Bin reaction vars
         , purity_q2_repulsed_bin = case_when(is.na(purity_q2_repulsed) ~ NA_real_
                                              , purity_q2_repulsed %in% c("None at all", "A little") ~ 0
                                              , purity_q2_repulsed %in% c("A moderate amount", "A great deal", "A lot") ~ 1
                                              , TRUE ~ NA_real_)
         , purity_q4_relieved_bin = case_when(is.na(purity_q4_relieved) ~ NA_real_
                                              , purity_q4_relieved %in% c("None at all", "A little") ~ 0
                                              , purity_q4_relieved %in% c("A moderate amount", "A great deal", "A lot") ~ 1
                                              , TRUE ~ NA_real_)
         , fairness_q2_pain_bin = case_when(is.na(fairness_q2_pain) ~ NA_real_
                                            , fairness_q2_pain %in% c("None at all", "A little") ~ 0
                                            , fairness_q2_pain %in% c("A moderate amount", "A great deal", "A lot") ~ 1
                                            , TRUE ~ NA_real_)
         , fairness_q4_relieved_bin = case_when(is.na(fairness_q4_relieved) ~ NA_real_
                                                , fairness_q4_relieved %in% c("None at all", "A little") ~ 0
                                                , fairness_q4_relieved %in% c("A moderate amount", "A great deal", "A lot") ~ 1
                                                , TRUE ~ NA_real_)
         , open_text_reaction = q3_fc2
         # Factor variables
         , ideology = factor(polispect, levels = ideology_levels)
         , ideology_bin = case_when(is.na(ideology) ~ "missing"
                                    , ideology == "Very Liberal" ~ "liberal"
                                    , ideology == "Lean Liberal" ~ "liberal"
                                    , ideology == "Liberal" ~ "liberal"
                                    , ideology == "Very Conservative" ~ "conservative"
                                    , ideology == "Lean Conservative" ~ "conservative"
                                    , ideology == "Conservative" ~ "conservative"
                                    , TRUE ~ "moderate")
         # UBI/Outcome
         , ubi_group = factor(ubi_2_nps_group, levels = ubi_group_levels)
         , ubi_familiarity = factor(ubi_f, levels = ubi_familiarity_levels)
         , ubi_familiarity_bin = case_when(is.na(ubi_f) ~ NA_real_
                                           , ubi_f == "Not familiar at all" ~ 0
                                           , TRUE ~ 1)
         , ubi_number = as.numeric(ubi_2)
  )
         

results_clean = results_full %>%
  select(prolific_pid, panel, arm, node, arm_level
         , ideology, ideology_bin, age, gender, urban, employment_status, student_status
         , purity_q1_self, purity_q2_repulsed, purity_q3_injustice, purity_q4_relieved
         , fairness_q1_self, fairness_q2_pain, fairness_q3_injustice, fairness_q4_relieved
         , purity_q2_repulsed_bin, purity_q4_relieved_bin, fairness_q2_pain_bin, fairness_q4_relieved_bin
         , open_text_reaction
         , ubi_number, ubi_group, ubi_familiarity, ubi_familiarity_bin)
```

## Exploratory Analysis  
_[[TBD]]_  

### Study Setup  

```{r exploratory, echo = FALSE, fig.height = 4, fig.width = 4, fig.align="center", fig.cap="Study Setup"}
nodes = data.frame(
  id = 1:8
  , group = c("ideology", "ideology"
              , "treatment"
              , "control"
              , "purity", "purity"
              , "fairness", "fairness"
              )
  , label = c("All Liberals", "All Conservatives"
              , "Treatment"
              , "Control"
              , "Purity Base"
              , "Purity Extension"
              , "Fairness Base"
              , "Fairness Extension"
              )
  , level = c(1, 1, 2, 2, 3, 4, 3, 4)
  , shape = rep("box", 8)
  )

edges = data.frame(
  from = c(1, 2, 1, 2, 3, 3, 5, 7)
  , to = c(3, 3, 4, 4, 5, 7, 6, 8)
  , dashes = c(rep(FALSE, 6), rep(TRUE, 2))
  )

visNetwork(nodes, edges) %>%
  visEdges(arrows = "to") %>% 
  visHierarchicalLayout() 
```

### Demographics  

```{r exploratory_demographics, fig.height = 8, fig.width = 8, fig.align="center", fig.cap="Demographics"}

grpstackbar_plot = ggplot() +
  facet_grid( ~ ideology_bin) +
  scale_fill_brewer(type = "div", palette = 5, direction = -1, aesthetics = "fill") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Ideology
plot_ideology = grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(ideology, ideology_bin) %>% summarise(count = n())
           , aes(x = ideology, y = count, fill = ideology), stat = "identity") + 
  theme(legend.position = "left", axis.text.x=element_blank(), legend.text=element_text(size = 8))
# Age
plot_age = grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(age, ideology, ideology_bin) %>% summarise(count = n())
           , aes(x = age, y = count, fill = ideology), stat = "identity", show.legend = FALSE)
# Gender
plot_gender = grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(gender, ideology, ideology_bin) %>% summarise(count = n())
           , aes(x = gender, y = count, fill = ideology), stat = "identity", show.legend = FALSE)
# Urban
plot_urban = grpstackbar_plot +
  geom_bar(data = results_clean %>%  group_by(urban, ideology, ideology_bin) %>% summarise(count = n())
           , aes(x = urban, y = count, fill = ideology), stat = "identity", show.legend = FALSE)

grid.arrange(plot_ideology, plot_gender 
             , plot_age, plot_urban
             , nrow = 2)
```

Example reference to r cell _\autoref{fig:exploratory_demographics}_ shows _[[TBD]]_   

### Reactions  

```{r exploratory_reactions, fig.height = 8, fig.width = 8, fig.align="center", fig.cap="Reactions"}
results_response = results_clean %>%
  select(panel, arm
         , purity_q1_self, purity_q2_repulsed, purity_q3_injustice, purity_q4_relieved
         , fairness_q1_self, fairness_q2_pain, fairness_q3_injustice, fairness_q4_relieved) %>%
  gather(prompt, value, -panel, -arm) %>%
  filter(!is.na(value)) %>%
  group_by(panel, arm, prompt, value) %>% summarise(count = n()) %>%
  mutate(response = factor(value, levels = response_levels))

ggplot(data = results_response
       , aes(x = prompt, y = response, fill = count)) +
  geom_tile() +
  facet_grid(rows = vars(arm), cols = vars(panel)) +
  scale_fill_distiller(direction = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r exploratory_reactions_bin, fig.height = 8, fig.width = 8, fig.align="center", fig.cap="Reactions (Bin)"}
results_response_bin = results_clean %>%
  select(ideology_bin, arm
         , purity_q2_repulsed_bin, purity_q4_relieved_bin
         , fairness_q2_pain_bin, fairness_q4_relieved_bin) %>%
  gather(prompt, value, -ideology_bin, -arm) %>%
  filter(!is.na(value)) %>%
  group_by(ideology_bin, arm, prompt, value) %>% 
  summarise(count = n()) %>%
  group_by(ideology_bin, arm) %>% 
  mutate(count_total_cohort = sum(count)
         , count_share = count/count_total_cohort
         , reaction = case_when(value == 1 ~ "effected"
                                , value == 0 ~ "not_effected"
                                , TRUE ~ NA_character_))

ggplot(data = results_response_bin
       , aes(x = prompt, y = reaction, fill = count_share)) +
  geom_tile() +
  facet_grid(rows = vars(arm), cols = vars(ideology_bin)) +
  scale_fill_distiller(direction = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Outcome  

```{r exploratory_outcome, fig.height = 8, fig.width = 8, fig.align="center", fig.cap="Outcomes"}
# Histogram of familiarity
plot_familiarity = ggplot(data = results_clean %>% group_by(ubi_familiarity, ideology, ideology_bin) %>% summarise(count = n())
       , aes(x = ubi_familiarity, y = count, fill = ideology)) +
  geom_bar(stat="identity", show.legend = FALSE) +
  facet_grid( ~ ideology_bin) +
  scale_fill_brewer(type = "div", palette = 5, direction = -1, aesthetics = "fill") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Heat map of number UBI like
plot_ubi = ggplot(data = results_clean %>% group_by(ubi_familiarity, ideology) %>% summarise(ubi_number_avg = mean(ubi_number))
       , aes(x = ubi_familiarity, y = ideology, fill = ubi_number_avg)) +
  geom_tile() +
  scale_fill_distiller(direction = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)
        , legend.position = "right")

grid.arrange(plot_familiarity, plot_ubi
              , nrow = 2)
```

\pagebreak

# Methodology  

## Model 1  

**Independent variable**  

**Dependent variable**  

**Model specification**  

_[[TBD]]_. (see _\autoref{fig:model_1_explore}_)

```{r lm_function}
my_lm_calcs = function(lm_in, clusters_in){
  # Robust
  vcov_robust = vcovHC(lm_in)
  se_robust = sqrt(diag(vcov_robust))
  # Cluster
  if(length(clusters_in) > 1){
    vcov_cluster = cluster.vcov(lm_in, clusters_in)
    se_cluster = sqrt(diag(vcov_cluster))
  } else {
    vcov_cluster = NA
    se_cluster = NA
  }
  # Output
  lm_out = list(lm = lm_in
                , vcov_robust = vcov_robust
                , se_robust = se_robust
                , vcov_cluster = vcov_cluster
                , se_cluster = se_cluster
  )
  return(lm_out)
}
```

```{r}
# Summaries
all_data = data.table(results_full)
all_data[, ideology_bin := case_when(is.na(ideology) ~ "missing",
                                           ideology=="Very Liberal" ~ "liberal",
                                           ideology=="Lean Liberal" ~ "liberal",
                                           ideology=="Liberal" ~ "liberal",
                                           ideology=="Very Conservative" ~ "conservative",
                                           ideology=="Lean Conservative" ~ "conservative",
                                           ideology=="Conservative" ~ "conservative",
                                           TRUE ~ "moderate"), ]
all_data[, story := case_when(is.na(arm) ~ "missing",
                                           arm=="control" ~ "",
                                           arm=="purity_base" ~ "homeless",
                                           arm=="purity_extension" ~ "homeless-cleaned",
                                           arm=="fairness_base" ~ "bullying",
                                           arm=="fairness_extension" ~ "bullying-addressed",
                                           TRUE ~ "others"), ]
all_data[, FemaleReader := ifelse(gender!='Male', 1, 0), ]
all_data[, ubi_familiarity_dummy := ifelse(ubi_familiarity_bin!='yes', 1, 0), ]
all_data[, ubi := as.numeric(ubi_2), ]
all_data[ , .(ubi=mean(as.numeric(ubi_2)), .N), keyby=list(ideology_bin, story, FemaleReader, ubi_familiarity_bin) ]
```

```{r}
# augment model with results from coefteest and coefci using 
# the supplied variance/covariance matrix
apply_robust_estimates = function(model, vcovmatrix) {
  model$robust.coeftest = coeftest(model, vcov. = vcovmatrix)
  model$robust.estimate = model$robust.coeftest[, 'Estimate']
  model$robust.std.error = model$robust.coeftest[, 'Std. Error']
  model$robust.statistic = model$robust.coeftest[, 't value']
  model$robust.p.value = model$robust.coeftest[, 'Pr(>|t|)']
  model$robust.coefci = coefci(model, vcov. = vcovmatrix)
  model$robust.ci.low = model$robust.coefci[, "2.5 %"]
  model$robust.ci.high = model$robust.coefci[, "97.5 %"]
  model
}
# liberals - homeless story
hom_lib_mod<-all_data[ ideology_bin=='liberal' & story != 'bullying' & story != 'bullying-addressed',  lm(ubi~story*FemaleReader)]
hom_lib_mod<-apply_robust_estimates(hom_lib_mod, vcovHC(hom_lib_mod))
# conservatives - homeless story
hom_con_mod<-all_data[ ideology_bin=='conservative' & story != 'bullying' & story != 'bullying-addressed',  lm(ubi~story*FemaleReader)]
hom_con_mod<-apply_robust_estimates(hom_con_mod, vcovHC(hom_con_mod))
# liberals - jacket story
jac_lib_mod<-all_data[ ideology_bin=='liberal' & story != 'homeless' & story != 'homeless-cleaned',  lm(ubi~story*FemaleReader)]
jac_lib_mod<-apply_robust_estimates(jac_lib_mod, vcovHC(jac_lib_mod))
# conservatives - jacket story
jac_con_mod<-all_data[ ideology_bin=='conservative' & story != 'homeless' & story != 'homeless-cleaned',  lm(ubi~story*FemaleReader)]
jac_con_mod<-apply_robust_estimates(jac_con_mod, vcovHC(jac_con_mod))
stargazer(hom_lib_mod, hom_con_mod,
          type = 'text', 
          se = list(sqrt(diag(vcovHC(hom_lib_mod))),
                    sqrt(diag(vcovHC(hom_con_mod)))), 
          header=F,
          report=('v*c*sp'), 
          add.lines=list(c("Ideology", "Liberal", "Conservative")))
stargazer(jac_lib_mod, jac_con_mod,
          type = 'text', 
          se = list(sqrt(diag(vcovHC(jac_lib_mod))),
                    sqrt(diag(vcovHC(jac_con_mod)))), 
          header=F,
          report=('v*c*sp'), 
          add.lines=list(c("Ideology", "Liberal", "Conservative")))
```

```{r}
# augment model with results from coefteest and coefci using 
# the supplied variance/covariance matrix
# liberals - homeless story
hom_lib_mod_2<-all_data[ ideology_bin=='liberal' & story != 'bullying' & story != 'bullying-addressed',  lm(ubi~story*ubi_familiarity_bin)]
hom_lib_mod_2<-apply_robust_estimates(hom_lib_mod_2, vcovHC(hom_lib_mod_2))
# conservatives - homeless story
hom_con_mod_2<-all_data[ ideology_bin=='conservative' & story != 'bullying' & story != 'bullying-addressed',  lm(ubi~story*ubi_familiarity_bin)]
hom_con_mod_2<-apply_robust_estimates(hom_con_mod_2, vcovHC(hom_con_mod_2))
# liberals - jacket story
jac_lib_mod_2<-all_data[ ideology_bin=='liberal' & story != 'homeless' & story != 'homeless-cleaned',  lm(ubi~story*ubi_familiarity_bin)]
jac_lib_mod_2<-apply_robust_estimates(jac_lib_mod_2, vcovHC(jac_lib_mod_2))
# conservatives - jacket story
jac_con_mod_2<-all_data[ ideology_bin=='conservative' & story != 'homeless' & story != 'homeless-cleaned',  lm(ubi~story*ubi_familiarity_bin)]
jac_con_mod_2<-apply_robust_estimates(jac_con_mod_2, vcovHC(jac_con_mod_2))
stargazer(hom_lib_mod_2, hom_con_mod_2,
          type = 'text', 
          se = list(sqrt(diag(vcovHC(hom_lib_mod_2))),
                    sqrt(diag(vcovHC(hom_con_mod_2)))), 
          header=F,
          report=('v*c*sp'), 
          add.lines=list(c("Ideology", "Liberal", "Conservative")))
stargazer(jac_lib_mod_2, jac_con_mod_2,
          type = 'text', 
          se = list(sqrt(diag(vcovHC(jac_lib_mod_2))),
                    sqrt(diag(vcovHC(jac_con_mod_2)))), 
          header=F,
          report=('v*c*sp'), 
          add.lines=list(c("Ideology", "Liberal", "Conservative")))
```

```{r methodology_model_1_explore, fig.height = 3, fig.width = 4, fig.align="center", fig.cap="\\label{fig:model_1_explore}Model 1 - Exploratory Plot", results='asis'}
# Exploratory
results_armlibfair = results_clean %>% filter(ideology_bin == 'liberal' & grepl('fairness|control', arm))
results_armlibpure = results_clean %>% filter(ideology_bin == 'liberal' & grepl('purity|control', arm))
results_armconfair = results_clean %>% filter(ideology_bin == 'conservative' & grepl('fairness|control', arm))
results_armconpur = results_clean %>% filter(ideology_bin == 'conservative' & grepl('purity|control', arm))

model1_libfair = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level, data = results_armlibfair), clusters_in = NA)
model1_libpure = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level, data = results_armlibpure), clusters_in = NA)
model1_confair = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level, data = results_armconfair) , clusters_in = NA)
model1_conpure = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level, data = results_armconpur), clusters_in = NA)

stargazer(model1_libfair$lm, model1_libpure$lm
          , model1_confair$lm, model1_conpure$lm
          , type = stargazer_type, header = F
          , se = list(model1_libfair$se_robust, model1_libpure$se_robust
                      , model1_confair$se_robust, model1_conpure$se_robust)
          , title = "Moral Foundations Prelim Regression Specifications"
          , column.labels = c("Lib + Fair", "Lib + Purity"
                              , "Con + Fair", "Con + Purity")
          , notes = "HC Robust Standard Errors"
          , report = ('v*c*sp')
)
```

```{r fitted_resduals_model1, fig.width=8, fig.height=8, fig.align="center", fig.cap="Model 1 Arms 1-4 - Residuals vs. Fitted"}
par(mfrow=c(2,2))
which_in = 2
plot (model1_libfair$lm, which = which_in)
plot (model1_libpure$lm, which = which_in)
plot (model1_confair$lm, which = which_in)
plot (model1_conpure$lm, which = which_in)
```

```{r coef_model1, fig.width=6, fig.height=4, fig.align="center", fig.cap="Model 1 Arms 1-4 - Coefficients"}

arm_plot_df = function(model_in, group_in){
  baseline_val = model_in$lm$coefficients[1]
  
  arm_plot_df = data.frame(group = rep(group_in, 3)
                           , arm = c("control", "base", "extension")
                           , coef = model_in$lm$coefficients
                           , se = model_in$se_robust
  ) %>%
    mutate(baseline = baseline_val
           , ubi = case_when(arm == "control" ~ coef
                             , TRUE ~ coef + baseline))
  
  return(arm_plot_df)
}

arm_plot_libpure = arm_plot_df(model_in = model1_libpure, group_in = "liberal_pure")
arm_plot_libfair = arm_plot_df(model_in = model1_libfair, group_in = "liberal_fair")
arm_plot_conpure = arm_plot_df(model_in = model1_conpure, group_in = "conservative_pure")
arm_plot_confair = arm_plot_df(model_in = model1_confair, group_in = "conservative_fair")

ggplot() +
  geom_point(data = arm_plot_libpure, aes(x = baseline, y = ubi, shape = group, color = arm, size = 10)) +
  geom_point(data = arm_plot_libfair, aes(x = baseline, y = ubi, shape = group, color = arm, size = 10)) +
  geom_point(data = arm_plot_conpure, aes(x = baseline, y = ubi, shape = group, color = arm, size = 10)) + 
  geom_point(data = arm_plot_confair, aes(x = baseline, y = ubi, shape = group, color = arm, size = 10)) +
  geom_abline(slope = 1, intercept = 0)
```

```{r methodology_model_1_gender, results='asis'}

model1_libfair_gender = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level*gender, data = results_armlibfair), clusters_in = NA)
model1_libpure_gender = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level*gender, data = results_armlibpure), clusters_in = NA)
model1_confair_gender = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level*gender, data = results_armconfair) , clusters_in = NA)
model1_conpure_gender = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level*gender, data = results_armconpur), clusters_in = NA)

stargazer(model1_libfair_gender$lm, model1_libpure_gender$lm
          , model1_confair_gender$lm, model1_conpure_gender$lm
          , type = stargazer_type, header = F
          , se = list(model1_libfair_gender$se_robust, model1_libpure_gender$se_robust
                      , model1_confair_gender$se_robust, model1_conpure_gender$se_robust)
          , title = "Moral Foundations Prelim Regression Specifications"
          , column.labels = c("Lib + Fair", "Lib + Purity"
                              , "Con + Fair", "Con + Purity")
          , notes = "HC Robust Standard Errors"
          , report = ('v*c*sp')
)
```

```{r methodology_model_1_familiarity, results='asis'}

model1_libfair_familiarity = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level+ubi_familiarity_bin, data = results_armlibfair), clusters_in = NA)
model1_libpure_familiarity = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level+ubi_familiarity_bin, data = results_armlibpure), clusters_in = NA)
model1_confair_familiarity = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level+ubi_familiarity_bin, data = results_armconfair) , clusters_in = NA)
model1_conpure_familiarity = my_lm_calcs(lm_in = lm(ubi_number ~ arm_level+ubi_familiarity_bin, data = results_armconpur), clusters_in = NA)

stargazer(model1_libfair_familiarity$lm, model1_libpure_familiarity$lm
          , model1_confair_familiarity$lm, model1_conpure_familiarity$lm
          , type = stargazer_type, header = F
          , se = list(model1_libfair_familiarity$se_robust, model1_libpure_familiarity$se_robust
                      , model1_confair_familiarity$se_robust, model1_conpure_familiarity$se_robust)
          , title = "Moral Foundations Prelim Regression Specifications"
          , column.labels = c("Lib + Fair", "Lib + Purity"
                              , "Con + Fair", "Con + Purity")
          , notes = "HC Robust Standard Errors"
          , report = ('v*c*sp')
)
```

_[[Example Table]]_  

| Model | Specification | Interpretation | Figure |
| :--- | :------ | :-------- | :--- |
| Model 1 | _ubinumber~armlevel_ | $\Delta armlevel = \beta_1 \Delta ubinumber$ | _\autoref{fig:model_1_fitplots}_ |

```{r methodology_model_1_final, results='asis', fig.cap="\\label{fig:model_1_final}"}
# Stargazer
```

\pagebreak

# Results  

_[[TBD]]_  

\pagebreak

# Conclusion  

_[[TBD]]_  

\pagebreak

# Discussion

_[[TBD]]_  

## Limitations

_[[TBD]]_   

\pagebreak

# Technical Appendix

## Data Dictionary

| Variable Name | Variable | Values | Source | Notes |
| :---- | :-------- | :-------- | :---------- | :----- |
| prolific_pid |||||
| panel |||||
| arm |||||
| node |||||
| arm_level |||||
| ideology |||||
| ideology_bin |||||
| age |||||
| gender |||||
| urban |||||
| employment_status |||||
| student_status |||||
| purity_q1_self |||||
| purity_q2_repulsed |||||
| purity_q3_injustice |||||
| purity_q4_relieved |||||
| fairness_q1_self |||||
| fairness_q2_pain |||||
| fairness_q3_injustice |||||
| fairness_q4_relieved |||||
| open_text_reaction |||||
| ubi_number | UBI Number | Integer 0-10 |||
| ubi_group |||||
| ubi_familiarity |||||
| ubi_familiarity_bin |||||

\pagebreak

## Exploratory Data Analysis

**Additional steps taken not included in the body of the report**  

_[[TBD]]_  
